---
title: "Children use one-to-one correspondence to establish equality after learning to count"
bibliography: citations.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{Rose M. Schneider \and David Barner \\
         $\{$roschnei, dbarner$\}$ @ucsd.edu \\ Department of Psychology \\ University of California, San Diego}
    
abstract: >
  Humans make frequent and powerful use of external symbols to express number exactly, leading some to question whether exact number concepts are *only* available through the acquisition of symbolic number systems. Although prior work has addressed this longstanding debate on the relationship between language and thought in innumerate populations and semi-numerate children, it has frequently produced conflicting results, leaving the origin of exact number concepts unclear. Here, we return to this question by replicating methods previously used to assess exact number knowledge in innumerate groups, such as the Pirahã, with a large sample of semi-numerate US toddlers. We replicate previous findings from both innumerate cultures and developmental studies showing that numeracy is linked to the concept of exact number. However, we also find evidence that this knowledge is surprisingly fragile even amongst numerate children, suggesting that numeracy alone does not guarantee a full understanding of exactness.
keywords: >
    Number; language; cognitive development; conceptual development
    
output: cogsci2016::cogsci_paper
final-submission: \cogscifinalcopy
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r setup, include = FALSE}
rm(list = ls())
load("../../../Data/one-one_cleaned.RData") #study 1
load("../../../../Study 2.1/Data/one-one_control_cleaned.RData") #study 2
load("../../../../Study 2.1/Data/one-one_control_check_cleaned.Rdata") #study 2 final answer and memory check
library(tidyverse)
library(magrittr)
library(langcog)
library(lme4)
library(stringr)
library(RColorBrewer)
library(ggthemes)
library(tidylog)

#filtering function
'%!in%' <- function(x,y)!('%in%'(x,y))

#set root
require("knitr")
```

```{r data_manips, include = FALSE}
all.data %<>%
  filter(Task == "Parallel" | Task == "Orthogonal", 
         Trial_number != "Training")%>%
  mutate(Task_item = as.numeric(as.character(Task_item)), 
         Response = as.numeric(as.character(Response)), 
         Age = as.numeric(as.character(Age)))
         
all.data.study2 %<>%
  filter(Task == "Set-matching", 
         Trial_number != "Training")%>%
  mutate(Task_item = as.numeric(as.character(Task_item)), 
         Response = as.numeric(as.character(Response)), 
         Age = as.numeric(as.character(Age)))
```

```{r}
# #counting attempts by knower level
counting <- all.data %>%
  filter(Task == "Parallel" |
           Task == "Orthogonal",
         Trial_number != "Training")%>%
  droplevels()%>%
  mutate(Counting_validate = as.numeric(as.character(Counting_validate)),
         Counting_validate = ifelse(is.na(Counting_validate), 0, Counting_validate))%>%
  group_by(CP_subset)%>%
  summarise(count_attempts = sum(Counting_validate),
            total = n())%>%
  mutate(prop = count_attempts/total)
#   
# #number language
number <- all.data %>%
  filter(Task == "Parallel" |
           Task == "Orthogonal")%>%
  droplevels()%>%
  mutate(Num_lang = as.numeric(as.character(Num_lang)),
         Num_lang = ifelse(is.na(Num_lang), 0, Num_lang))%>%
  group_by(Task, CP_subset)%>%
  summarise(number_language = sum(Num_lang),
            total = n())%>%
  mutate(prop = number_language/total)
```

# Introduction
Human numerical abilities are built upon a foundation of core cognitive mechanisms shared with nonhuman animals; humans, however, enjoy a concept of number that is both \emph{exact} and \emph{unbounded}, and far exceeds the limits of what these foundational systems afford [@carey2019]. Humans are distinct from other animals in another critical sense, however, in that they regularly use symbols to externalize these exact number representations. This relationship between the uniquely human capacities of symbolic expression and exact number representation has prompted an enduring debate about whether representations of exactness are dependent upon knowledge of a symbolic number system. 

There is agreement that, even without access to exact number language, humans possess two numerical representation mechanisms: the Parallel Individuation (PI) system, which can represent small sets (3-4), and the Approximate Number System (ANS), which offers imprecise representations of large quantities [@feigenson2004]. While both mechanisms are available early in life [@wynn1992addition; @izard2009] and are refined over development, even together in their mature form they are incapable of supporting large exact number representations. Although the PI system furnishes precise representations, it is limited to quantities of 3 or 4, and while the ANS supports large number representations, they are imprecise. In particular, a key failing of the ANS in capturing integer properties is that it operates as a function of the ratio between two quantities (i.e., Weber's law). Thus, the ANS cannot detect quantity differences when ratios are sufficiently small (e.g., 9:10).

There is some evidence from innumerate cultures that, without access to linguistic number, human numerical representations are limited to these two systems and do not permit representations of exactness. @gordon2004 investigated how the Pirahã, an indigenous Amazonian society with no exact number language, perform on a task requiring them to create a set of objects matching an experimenter's. In the simplest version of this task, the experimenter placed their set directly above the Pirahã's. The logic of this task as a test of exact number stems from Hume's Principle -- that exact equality between sets can only be established by putting them into one-to-one correspondence. Therefore, if a participant understands that number \emph{can} be represented exactly, then they should use one-to-one correspondence to generate matches for \emph{all} numerosities. On the other hand, if no such knowledge exists, then their matches for large quantities should show the ratio-dependent signatures of the ANS. 

Using this diagnostic, @gordon2004, and later @everett2012, found that the Pirahã succeeded for items within the PI range, but approximated for larger quantities, even when one-to-one correspondence could be easily established. While these results seem to suggest the concept of exact equality is linked to symbolic number language, they were contradicted by @frank2008, who found that the Pirahã \emph{could} deploy one-to-one correspondence for all numerosities, although they were less likely to do so when this correspondence was more difficult to establish (e.g., if the experimenter's set was hidden after a brief presentation). Due to the challenges associated with testing remote populations such as the Pirahã, these discrepant findings are difficult to adjudicate and resolve.

<!-- These discrepant findings are difficult to resolve for several reasons,  leaving the origins of exact number concepts unclear. First, many innumerate groups, such as the Pirahã, live in remote regions and are sometimes under the protection of local governments, making studies difficult to both conduct and to replicate. Second, because of difficulties accessing these groups stemming both from their remote locations, and from linguistic and cultural differences that may impede testing, small samples often used in these studies. Finally, this work fails to pinpoint symbolic number language as the source of exact number concepts, leaving open the possibility that innumerate individuals .  -->

The origin of exact number concepts has also been explored in another semi-numerate population: young children. Although most children in industrialized cultures hear number language early in life, they do not begin to acquire the meanings of number words until around 2.5 years of age [@wynn1992]. Children begin the learning process by acquiring the meanings of small number words -- e.g., \emph{one, two, three, four} -- one at a time, in sequential order, over a period of many months, and do not seem to understand their relationship to the count list. Around 4 years of age, however, children progress beyond this "subset knower" stage, and acquire some form of the “Cardinal Principle” (CP). These "CP-knowers" understand how to use the count routine to generate sets for larger number words [@wynn1992], and they seem to possess a qualitatively different understanding of number relative to subset knowers [@sarnecka2008]. The developmental trajectory associated with children’s number acquisition is remarkably consistent [@mollicainprep], and can be reliably assessed in the lab, offering a compelling case study in which to explore the origin of exact number concepts and their relationship to symbolic number. 

Recent investigations of whether children can reason about large exact number prior to CP acquisition have produced mixed results. For instance, @izard2014 found that subset knowers could track equality between 6 puppets placed on 6 tree branches, although they failed to do so if the perceptual identity of the puppets changed. Similarly, @sarnecka2013 found that subset knowers could use one-to-one correspondence to determine whether two sets of 6 were "just the same." Finally, @jaraettinger2017 found that subset knowers could track changes to equality between two large sets, indicating a fairly robust understanding of exact equality. In contrast, other work has shown that subset knowers fail to spontaneously use one-to-one correspondence to establish equality, even for sets within their PI range. For example, @negen2009 found that children's ability to match sets <5 cumulatively increased as a function of known number words. Additionally, @mix1999 and @mix1996 found that subset knowers' ability to match sets of 2-4 was significantly affected by their perceptual similarity. 

While the developmental literature suggests that subset knowers may have some partial understanding of Hume's Principle, this work is limited in several ways. First, much of the current literature focuses on sets within the PI range, and does not compare performance between small and large numerosities. Second, it leaves open whether subset knowers' successes for larger quantities stems from understanding the relationship between one-to-one correspondence and exact number, or because this relationship was highlighted within these paradigms. Finally, comparisons of nonsymbolic one-to-one knowledge between subset and CP-knowers are limited, leaving open the question of whether this knowledge is affected by learning the significance of the count routine. 

Here, we address these outstanding questions in the developmental literature along with a set of contested findings from innumerate cultures. We adapt methods previously used in work with the Pirahã [@everett2012; @frank2008; @gordon2004] to investigate exact number knowledge in a large group of 3- to 5-year-old children. Specifically, we use the set-matching task to explore whether young children recognize the non-symbolic relationship between one-to-one correspondence and exact equality, and how this knowledge is related to their acquisition of symbolic number. In Experiment 1, we replicate findings from innumerate cultures and some of the developmental literature that numeracy is significantly related to performance on a set-matching task. In Experiment 2, we rule out one alternative hypothesis for CP-knowers' increased accuracy in comparison to subset knowers. Surprisingly, we find that while CP-knowers outperformed subset knowers in both Experiments, their performance was far from ceiling. Together, our findings suggest that the relationship between one-to-one correspondence and exact number becomes more salient to children after they have acquired the CP, and that this knowledge may continue to develop for some time after children achieve this level of numeracy.

# Experiment 1
## Method
This study was pre-registered on OSF (https://osf.io/3wta2), and all methodological and analytical choices were as preregistered, unless stated otherwise in-text.

### Participants
```{r demographics, include= FALSE}
#study 1
demos <- all.data %>%
  distinct(SID, Age, CP_subset)%>%
  group_by(CP_subset)%>%
  summarise(n = n(),
            mean_age = mean(Age, na.rm = TRUE),
            sd_age = sd(Age, na.rm = TRUE))%>%
  group_by()%>%
  mutate(total.n = sum(n))

#min max mean sd
min_age = min(all.data$Age, na.rm = TRUE)
max_age = max(all.data$Age, na.rm = TRUE)
mean_age = mean(all.data$Age, na.rm = TRUE)
sd_age= sd(all.data$Age, na.rm = TRUE)
```

Our final analyzable sample included `r demos$total.n[1]` children ($M_{age}$ = `r round(mean_age, 2)` years, $SD_{age}$ = `r round(sd_age, 2)` years, range = `r round(min_age, 2)` - `r round(max_age, 2)` years) recruited from local preschools and the surround community in San Diego, California, USA. In this sample, `r demos$n[1]` were identified as CP-knowers, while the remaining `r demos$n[2]` were classified as subset knowers. 

## Procedure
### Set-matching
This task, modeled on @gordon2004, was framed as a "matching game." Children were presented with a 6"x30" blue cardboard rectangle and a container with 15 fish. The experimenter introduced the game by saying, "Let's play a matching game. Do you know what matching is? Matching is when you make things look the same. So, in this game, you're going to make things look like each other." The experimenter explained that the child could put their fish in their pond. Next, the experimenter then placed another blue board with one plastic fish glued to the center directly above the child's and said, "Using your fish, can you make your pond look like my pond?" 

In an effort to replicate the methods of @gordon2004 as closely as possible, and to obtain a measure of children's unprompted attention to exactness, the experimenter did not explicitly direct children to attend to number when giving either task instructions or feedback. One deviation from @gordon2004 was the inclusion of two training trials with 1 and 2 fish (on the experimenter's board), during which the children received non-numerical feedback to ensure that they understood the purpose of the task (e.g., "Look! These ponds match, because there is a fish here, and a fish here!").  

Boards were presented to children either in a Parallel or Orthogonal orientation, based on @gordon2004. In the Parallel orientation the experimenter's board was was placed directly above the child's, such that one-to-one correspondence was a readily available strategy for solving the task. In the Orthogonal orientation the experimenter's board was placed perpendicularly to the right of the child's, requiring a spatial transformation of one-to-one correspondence. All children received tasks in both orientations, with Parallel trials presented before Orthogonal trials.

To test whether children's ability to use one-to-one correspondence was affected by the identity of sets [@mix1999; @mix1996], we manipulated the similarity of the fish relative to the experimenter's between subjects. Half of the children were randomly assigned to the Identical condition, in which fish were the same for both the experimenter and the child, and half were assigned to the Non-identical condition, in which fish where were matched on relative size, but were different varieties. 

Training trials were presented for both the Parallel and Orthogonal orientations in a fixed order (1, then 2). After passing these training trials, children received 5 test trials in both board orientations with small (3, 4) and large (6, 8, and 10) quantities with neutral feedback. Trial order was fixed for the Parallel (3, 4, 10, 8, and 6) and Orthogonal (4, 3, 8, 10, and 6) orientations. Fish on the experimenter's boards were always approximately 1" apart, regardless of set size; although the set of 10 was spread across the majority of the board, the maximum number of fish (15) could still be placed on the board with approximately .25" separation. 

Children who attempted to count were immediately stopped and told "This isn't a counting game - this is just a matching game!" Counting attempts were relatively rare: In both conditions, CP-knowers attempted counts on `r counting$count_attempts[1]`/`r counting$total[1]` trials, while subset knowers attempted counts `r counting$count_attempts[2]`/`r counting$total[2]` trials.

```{r accuracy_vis, fig.pos = "t", fig.width=3.3, fig.height=1.9, fig.align = "center", fig.cap = "Mean accuracy on the set-matching tasks by CP-knower level. Error bars represent 95\\% confidence intervals computer by nonparametric bootstrap."}
all.data %>%
  filter(Task == "Parallel" | Task == "Orthogonal", 
         Trial_number != "Training")%>%
  mutate(Task_item = factor(Task_item, levels = c("3", "4",  
                                                  "6", "8", "10")), 
         Correct = as.numeric(as.character(Correct)))%>%
  group_by(Numerosity, Task, Task_item, CP_subset)%>%
    multi_boot_standard("Correct", na.rm = TRUE)%>%
  ggplot(aes(x = Task_item, y = mean, colour = CP_subset, group = interaction(Numerosity, CP_subset))) +
  geom_point(size = 1.5) + 
  geom_line() +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
                width = .1, 
                show.legend = FALSE) +
  theme_bw(base_size = 10) + 
  facet_grid(~factor(Task, levels = c("Parallel", "Orthogonal")), scale = "free_x") +
  theme( 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        legend.title = element_blank(), 
        legend.position = c(.85, .75),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-10,-10,-10,-10)) +
  labs(x = "Set size", y = "Mean accuracy") +
  scale_colour_brewer(palette = "Dark2") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(color= "Knower Level")
```

### Give-N
Children's CP knowledge was assessed using an abbreviated version of a titrated Give-N [@wynn1992]. The experimenter gave the child a plate and 10 plastic objects (e.g., bears, apples, buttons), and asked the child to place some number on the plate. After children placed some number of objects on the plate and indicated that they were finished, the experimenter asked, "Is that \emph{N}? Can you count and make sure?" If the child answered in the negative, they were permitted to fix the set. If children successfully generated a given \emph{N}, they were asked for \emph{N}+1 on the next trial; otherwise, they were asked for \emph{N}-1. Children were considered CP-knowers if they were able to generate sets of 6 (the maximum number tested) at least 2 out of 3 times when requested. Children were classified as subset knowers if they gave another \emph{N} correctly at least two of three times, and did not give that \emph{N} more than once for another number, as in @wynn1992.  

## Results and Discussion
```{r accuracy_df, include = FALSE}
model.df <- all.data %>%
  filter(Task == "Parallel" | Task == "Orthogonal", 
         Trial_number != "Training")%>%
  mutate(Task_item = as.numeric(as.character(Task_item)), 
         Response = as.numeric(as.character(Response)), 
         abs_error = abs(Task_item - Response), 
         highest_count = as.numeric(as.character(highest_count)), 
         age.c = as.vector(scale(Age, center = TRUE, scale=TRUE)), 
         Task_item.c = as.vector(scale(Task_item, center = TRUE, scale=TRUE)), 
         abs_error.c = as.vector(scale(abs_error, center = TRUE, scale=TRUE)), 
         highest_count.c = as.vector(scale(highest_count, center = TRUE, scale = TRUE)),
         count_proficiency.c = as.vector(scale(count_proficiency, center = TRUE, scale = TRUE)),
         Correct = as.numeric(as.character(Correct)), 
         CP_subset = factor(CP_subset, levels = c("Subset", "CP")))
```

```{r cp_overall_accuracy, include = FALSE}
### MAIN REPORTED MODEL ###
#create a base model that includes numerosity and task
overall.acc.base <- glmer(Correct ~ Task_item.c + Task + age.c + (1|SID), 
                          family = "binomial", data = model.df, 
                          control=glmerControl(optimizer="bobyqa",
                          optCtrl=list(maxfun=2e4)))

#add CP_subset-knower status
overall.acc.kl <- glmer(Correct ~ CP_subset + Task_item.c + Task + age.c + (1|SID), 
                          family = "binomial", data = model.df, 
                          control=glmerControl(optimizer="bobyqa",
                          optCtrl=list(maxfun=2e4)))

#now add interaction
overall.acc.kl.int <- glmer(Correct ~ CP_subset*Task_item.c + Task + age.c + (1|SID), 
                          family = "binomial", data = model.df, 
                          control=glmerControl(optimizer="bobyqa",
                          optCtrl=list(maxfun=2e4)))

#compare
anova.cp.overall <- anova(overall.acc.base, overall.acc.kl, overall.acc.kl.int, test = 'LRT') ## main effect of numerosity, task, CP-knowledge, and age 

cp.acc.final <- summary(overall.acc.kl)

### FOLLOW UP TEST FOR 3 WAY INTERACTION BETWEEN SET SIZE, ORIENTATION, AND CP ###
## FIRST, test for interaction between task and set size
#base model with interaction between numerosity and task
three_way.base <- glmer(Correct ~ Task_item.c*Task + age.c + (1|SID), 
                          family = "binomial", data = model.df, 
                          control=glmerControl(optimizer="bobyqa",
                          optCtrl=list(maxfun=2e4)))
#compare to overall.acc
anova(overall.acc.base, three_way.base, test = 'lrt') # this interaction does not improve the fit of the model

### Next, test for interaction between orientation, cp, and set size
## main effects
three_way.base.full <- glmer(Correct ~  CP_subset + Task + Task_item.c + age.c + (1|SID), 
                          family = "binomial", data = model.df, 
                          control=glmerControl(optimizer="bobyqa",
                          optCtrl=list(maxfun=2e4)))

three_way.2int <- glmer(Correct ~  CP_subset*Task + Task_item.c + age.c + (1|SID), 
                          family = "binomial", data = model.df, 
                          control=glmerControl(optimizer="bobyqa",
                          optCtrl=list(maxfun=2e4)))
anova(three_way.base.full, three_way.2int, test= 'lrt') #there is a significant interaction with task and CP 

##full 3-way interaction between task, cp, and set size
three_way.full <- glmer(Correct ~  CP_subset*Task*Task_item.c + age.c + (1|SID), 
                          family = "binomial", data = model.df, 
                          control=glmerControl(optimizer="bobyqa",
                          optCtrl=list(maxfun=2e4)))
anova(three_way.base.full, three_way.full, test= 'lrt') # significant interaction between set size, task, and cp knower status

#### IDENTITY ANALYSES - FINAL REPORTED MODEL ####
#base
overall.acc.kl <- glmer(Correct ~ CP_subset + Task_item.c + Task + age.c + (1|SID), 
                          family = "binomial", data = model.df, 
                          control=glmerControl(optimizer="bobyqa",
                          optCtrl=list(maxfun=2e4)))

ident.main.effect.kl <- glmer(Correct ~ Condition + CP_subset + Task_item.c + Task + age.c + (1|SID), 
                          family = "binomial", data = model.df, 
                          control=glmerControl(optimizer="bobyqa",
                          optCtrl=list(maxfun=2e4)))

ident.int.kl <- glmer(Correct ~ Condition*CP_subset + Task_item.c + Task + age.c + (1|SID), 
                          family = "binomial", data = model.df, 
                          control=glmerControl(optimizer="bobyqa",
                          optCtrl=list(maxfun=2e4)))

anova.ident.acc <- anova(overall.acc.kl, ident.main.effect.kl, ident.int.kl, test = 'LRT')

ident.final <- summary(ident.int.kl)
car::Anova(ident.int.kl)
```

```{r error_df, include = FALSE}
error.df <- all.data %>%
  filter(Task == "Parallel" | Task == "Orthogonal", 
         Trial_number != "Training", 
         Correct == "0")%>%
  droplevels()%>%
  mutate(Task_item = as.numeric(as.character(Task_item)), 
         Response = as.numeric(as.character(Response)), 
         abs_error = abs(Task_item-Response))
```

```{r error_vis, fig.pos = "tb", fig.width=3.3, fig.height=1.9, fig.align = "center", fig.cap = "Mean absolute error for incorrect trials on the set-matching tasks by CP-knower level. Error bars represent 95\\% confidence intervals computer by nonparametric bootstrap."}
error.df %>%
  mutate(Task_item = factor(Task_item, levels = c("3", "4",
                                                  "6", "8", "10")))%>%
  group_by(Numerosity, Task, Task_item, CP_subset)%>%
  multi_boot_standard("abs_error", na.rm = TRUE)%>%
  ggplot(aes(x = Task_item, y = mean, colour = CP_subset, group = interaction(Numerosity, CP_subset))) +
  geom_point(size = 1.5) +
  geom_line() +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),
                width = .1,
                show.legend = FALSE) +
  theme_bw(base_size = 10) +
  facet_grid(~factor(Task, levels = c("Parallel", "Orthogonal")), scale = "free_x") +
  theme(panel.grid = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.12, 0.75),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,0,0)) +
  labs(x = "Set size", y = "Mean absolute error") +
  scale_colour_brewer(palette = "Dark2") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  +
  labs(color = "Knower Level")
```

```{r dist_responses, fig.env = "figure*", fig.pos = "h", fig.width = 7.1, fig.height = 2.3, fig.align = "center", set.cap.width = T, num.cols = 2, fig.cap = "Frequency of set-size response (x-axis) for each target size in the Parallel condition, grouped by CP knowledge."}

all.data %>%
  filter(Task == "Parallel")%>%
  mutate(Task_item = as.numeric(as.character(Task_item)), 
         Response = as.numeric(as.character(Response)))%>%
  filter(Task_item > 2)%>%
  group_by(CP_subset, Task_item, Response)%>%
  # summarise(n = n()) %>%
  ggplot(aes(x = Response, fill = CP_subset)) +
  geom_vline(aes(xintercept = Task_item), linetype = "dashed", size = .3) +
  geom_histogram(size =1) + 
  theme_bw(base_size = 9) +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1, size = 5.5), 
        panel.grid = element_blank()) + 
  scale_fill_brewer(palette = "Dark2") +
  facet_grid(CP_subset ~ Task_item) +
  scale_x_continuous(breaks = seq(1, 15, 1)) + 
  labs(x = 'Number of items given', y = 'Frequency') 
```

Our primary question was whether CP-knowers were more likely than subset knowers to generate exact matches for both large and small set sizes. To test this, we built a generalized linear mixed effects model (GLMM) predicting exact matches from CP-knower status, set size, orientation (Parallel/Orthogonal), and age, with a random effect of subject.\footnote{All mixed effects models were fit in \texttt{R} using the \texttt{lme4} package. The final model specification was: \texttt{Correct $\sim$ CP-knower status + Set size + Orientation + Age + ( 1 | subject)}. Although we pre-registered a model containing a CP-knower status x Set size interaction, a Likelihood Ratio Test indicated that this interaction did not improve the fit of the main effects model ($\chi^2$ = `r round(anova.cp.overall$Chisq[3], 2)`, \emph{p} = .21).} This model indicated that CP-knowers generated exact matches significantly more often than subset knowers overall ($\beta$ = `r round(cp.acc.final$coefficients[2], 2)`, \emph{p} < .0001; Figure \ref{fig:accuracy_vis}), even when controlling for age ($\beta$ = `r round(cp.acc.final$coefficients[5], 2)`, \emph{p} = .01). This final model also revealed decreased accuracy with increasing set sizes ($\beta$ = `r round(cp.acc.final$coefficients[3], 2)`, \emph{p} < .0001), and for Orthogonal trials ($\beta$ = -`r round(cp.acc.final$coefficients[4], 2)`, \emph{p} < .0001). Follow-up analyses found no interaction between set size and orientation ($\chi^2$ = 0.99, *p* = 0.32); however, there was a significant 3-way interaction between set size, orientation, and CP-knower status ($\chi^2$ = 12.5, *p* = 0.006), such that the difference in performance between subset and CP-knowers for increasing set sizes was greatest in Parallel, as opposed to Orthogonal, orientations ($\beta$ = 0.98, *p* = .002).   

We next tested whether, consistent with prior work [@mix1999], CP-knowers were more likely than subset knowers to ignore perceptual dissimilarities in this task by constructing another GLMM predicting an exact match from an interaction between CP-knower status and identity condition (Identical/Non-identical), orientation (Parallel/Orthogonal), set size, and age, with a random effect of subject. This model indicated a significant interaction between set identity and CP knowledge, with CP-knowers significantly more accurate than subset knowers in the Non-identical condition ($\beta$ = `r round(ident.final$coefficients[7], 2)`, \emph{p} = .002), which was again significant when controlling for age ($\beta$ = `r round(ident.final$coefficients[6], 2)`, \emph{p} = .007). In addition to these effects, this model again indicated decreased accuracy when boards were presented in the Orthogonal orientation ($\beta$ = -0.86, *p* < .0001) and with increasing set size ($\beta$ = -1.24, *p* < .0001). 

These analyses indicate that, when one-to-one correspondence was a readily available strategy for matching sets, CP-knowers were more likely than subset knowers to capitalize on this relationship in order to generate numerically equal matches, even when the two sets were perceptually dissimilar. When the boards were presented in an Orthogonal orientation, and one-to-one correspondence was less easily implemented, however, CP-knowers' performance for large numerosities was not appreciably different from subset knowers'. However, despite CP-knowers' increased accuracy for boards in the Parallel orientation, their knowledge of one-to-one's significance was strikingly limited, with overall accuracy for large set sizes only 42% and far below adult-like levels [@frank2008]. This surprisingly variable performance (Figure \ref{fig:dist_responses}) suggests that acquisition of the CP alone may not guarantee an understanding of exact equality and its relationship to one-to-one correspondence.

```{r error_model, include = FALSE}
#### MAIN REPORTED MODEL ####
#do CP-knowers have lower rates of absolute error?
error.model.df <- model.df %>%
  filter(Correct == 0)

#descriptives
## descriptive of error
error.model.df %>%
  group_by(CP_subset, Numerosity, Task)%>%
  summarise(mean_error = mean(abs_error), 
            sd_error = sd(abs_error), 
            median_error = median(abs_error))

#base model
overall.error.base <- lmer(abs_error ~ Task_item.c + Task + age.c + (1|SID), 
                           data = error.model.df)

#add kl
overall.error.kl <- lmer(abs_error ~ CP_subset + Task_item.c + Task + age.c + (1|SID), 
                           data = error.model.df)

#add interaction
overall.error.int <- lmer(abs_error ~ CP_subset*Task_item.c + Task + age.c + (1|SID), 
                           data = error.model.df)

#compare 
anova.error.overall <- anova(overall.error.base, overall.error.kl, overall.error.int, test = 'LRT') #subset-knowers have higher absolute error for greater set sizes; significantly lower error on parallel task

final.error <- summary(overall.error.kl)
car::Anova(overall.error.kl)

### FOLLOW UP 3 WAY INTERACTION ####
## first test for interaction between task item and task
two.error.base <- lmer(abs_error ~ Task_item.c*Task + age.c + (1|SID), 
                           data = error.model.df)
anova(overall.error.base, two.error.base, test = 'lrt') #significant interaction between task and task item

#add CP knowledge
two.error.cp<- lmer(abs_error ~ CP_subset + Task_item.c*Task + age.c + (1|SID), 
                           data = error.model.df)
anova(two.error.base, two.error.cp, test = 'lrt') #cp knowledge adds to this model
summary(two.error.cp)
##get p values
two.cp.z = -3.09
2*pnorm(abs(two.cp.z), lower.tail = F)

two.int.z = 2.15
2*pnorm(abs(two.int.z), lower.tail = F)

#three way interaction
three.error.full<- lmer(abs_error ~ CP_subset*Task_item.c*Task + age.c + (1|SID), 
                           data = error.model.df)
anova(two.error.cp, three.error.full, test = 'lrt') #no significant three-way interaction

##get p values
cp.z = -3.12
2*pnorm(abs(cp.z), lower.tail = F)

set.size.z = 5.155
2*pnorm(abs(set.size.z), lower.tail = F)

task.z = -4.172
2*pnorm(abs(task.z), lower.tail = F)


##What about identity? 
overall.error.kl <- lmer(abs_error ~ CP_subset + Task_item.c + Task + age.c + (1|SID), 
                           data = error.model.df)

ident.error.kl <- lmer(abs_error ~ Condition + CP_subset + Task_item.c + Task + age.c + (1|SID), 
                           data = error.model.df)

ident.int.error.kl <- lmer(abs_error ~ Condition*CP_subset + Task_item.c + Task + age.c + (1|SID), 
                           data = error.model.df)
anova.error.ident <- anova(overall.error.kl, ident.error.kl, ident.int.error.kl, test = 'LRT')
final.ident.error <- summary(ident.int.error.kl)
```

Next, we also investigated errors in children's matching as a less conservative signal for whether they were attempting a one-to-one match, even if they were not accurate. For these analyses, we specifically investigated differences between subset and CP-knowers' absolute error (|Target set - Response|) on incorrect trials, as well as their Coefficient of Variation (CoV). If children are attempting a one-to-one match, we should find that their responses are closer to the target set, resulting in lower rates of absolute error and lower CoVs.

We first analyzed differences between subset and CP-knowers' absolute error on incorrect trials with a linear mixed effects model predicting absolute error from CP-knower status, set size, orientation, and age, with a random effect of subject.\footnote{The final model specification was: \texttt{Absolute error $\sim$ CP-knower status + Set size + Orientation + Age + ( 1 | subject)}. Although we again pre-registered a model containing a CP-knower status x Set size interaction, we pruned this interaction after finding it did not improve the fit of the model ($\chi^2$ = 2.74, \emph{p} = .10).} Likelihood Ratio Tests indicated a main effect of CP knowledge ($\chi^2$(1) = `r round(anova.error.overall$Chisq[2], 2)`, \emph{p} = .004), with lower absolute error for CP-knowers' in comparison to subset knowers ($\beta$ = `r round(final.error$coefficients[2], 2)`, \emph{p} = .002), even when controlling for age ($\beta$ = `r round(final.error$coefficients[5], 2)`, \emph{p} = .10; Figure \ref{fig:error_vis}). Absolute error increased with set size ($\beta$ = `r round(final.error$coefficients[3], 2)`, \emph{p} < .0001), and in the Orthogonal orientation ($\beta$ = `r (round(final.error$coefficients[4], 2)/-1)`, \emph{p} < .0001). 

Once again, we found evidence that CP-knowers are less affected by perceptual dissimilarities when establishing numerical equality; a second linear mixed effects model predicting absolute error from an interaction of CP knowledge and Identity condition, set size, orientation, and age, with a random effect of participant showed a significant interaction between CP knowledge and Identity ($\chi^2$(1) = `r round(anova.error.ident$Chisq[3], 2)`, \emph{p} = .002), such that CP-knowers had significantly lower error on Non-identical trials in comparison to subset knowers ($\beta$ = `r round(final.ident.error$coefficients[7], 2)`, \emph{p} = .001). 

```{r covs, include = FALSE}
##Let's try comparing between parallel and orthogonal
tmp.cov <- all.data %>%
  filter(Task == "Parallel" | Task == "Orthogonal", 
         Trial_number != "Training")%>%
  mutate(Task_item = as.numeric(as.character(Task_item)), 
         Response = as.numeric(as.character(Response)))%>%
  mutate(single.cov = (sqrt((Task_item-Response)^2)/Task_item))

#large/small numerosities
tmp.cov %<>%
  mutate(Numerosity = factor(Numerosity, levels = c("Small", "Large")))

#add absolute error
tmp.cov %<>%
  mutate(abs.error = abs(Task_item - Response))

cor.test(tmp.cov$single.cov, tmp.cov$abs.error)

tmp.cov %>%
  ggplot(aes(x = single.cov, y = abs.error, color = CP_subset, group = CP_subset)) + 
  geom_point() + 
  geom_smooth(method = 'lm')

##descriptive
tmp.cov %>%
  group_by(CP_subset, Task)%>%
  summarise(mean.cov = mean(single.cov, na.rm = TRUE))

## t-test between Orthogonal and parallel for CP and subset knowers
cov.ms <- tmp.cov %>%
  filter(Task == "Parallel")%>%
  group_by(SID, CP_subset)%>%
  summarise(mean.cov = mean(single.cov))

# t.test(subset(cov.ms, CP_subset == "CP" & Task == "Parallel")$mean.cov, 
#        subset(cov.ms, CP_subset == "CP" & Task == "Orthogonal")$mean.cov, var.equal = TRUE)

t.test(subset(cov.ms, CP_subset == "CP")$mean.cov, 
       subset(cov.ms, CP_subset == "Subset")$mean.cov, var.equal = TRUE)

# t.test(subset(cov.ms, CP_subset == "Subset" & Task == "Parallel")$mean.cov, 
#        subset(cov.ms, CP_subset == "Subset" & Task == "Orthogonal")$mean.cov, var.equal = TRUE)

```

Finally, we also used children's CoV, which captures noise in participants' responses to a given set size\footnote{CoV was approximated as in Frank et al. (2012), with the formula $\sqrt{(t_i - r_i)^2}/t_i$, where $t$ is the target quantity, and $r$ is the child's response.} as an additional measure of error in this task. Mirroring our accuracy and error analyses above, CoVs were significantly lower for CP-knowers in comparison to subset knowers for trials in both the Parallel (*t*(142) = -5.73, *p* < .0001) and Orthogonal orientations (*t*(141) = -4.99, *p* < .0001). While the slope of CoV relative to target quantity has been used to identify whether participants are deploying a one-to-one or approximation strategy in previous set-matching work [@everett2012; @frank2012], this analysis is not appropriate for our dataset for several reasons. First, unlike in previous work, both the number of items that participants could use to match sets, as well the area in which they could be matched, were bounded, which truncated the full distribution of responses for larger sets and affected CoV approximations. Prior work has shown that these kinds of bounds preclude assessments of the kind of scalar variability associated with ANS [@wagner2019]. Second, accuracy in our task was much lower than in previous work, and more children seemed to default to error-prone heuristics to solve this task (e.g., many subset knowers gave the maximum number of fish for large sets), yielding noisier CoV estimates. Due to these considerations, we cannot use CoV to make inferences about whether children were using one-to-one correspondence or approximation to solve this task.

Together, the results of our accuracy and error analyses broadly replicate the finding that numeracy is significantly related to the availability of exact number concepts. Similar to the Pirahã, and consistent with developmental work showing set-matching failures prior to CP acquisition, we found that although subset knowers were generally accurate for sets within their PI range, they were more less likely to generate an exact match for large numerosities. In contrast, CP-knowers were significantly more accurate in comparison to subset knowers for these larger numerosities, with their pattern of errors suggesting that a majority of children in this group were potentially attempting to deploy one-to-one correspondence. CP-knowers' performance was far from ceiling, however, and reflected some striking limitations. We return to this novel finding in the General Discussion. 

# Experiment 2
In Experiment 1, we found that CP-knowers were much more likely than subset knowers to establish exact equality between two large quantities. One possible reason for CP-knowers outperforming subset knowers in this task, however, is that they might have subvocally counted the experimenter's set and used it to generate a match. Experiment 2 was designed to test for this possibility.

## Method
This study was pre-registered on OSF (https://osf.io/pj4zy), and all methodological and analytical choices were as preregistered, unless stated otherwise in-text.

```{r study_2_participants, include = FALSE}
#study 2
demos.2 <- all.data.study2 %>%
  distinct(SID, Age, CP_subset)%>%
  group_by(CP_subset)%>%
  summarise(n = n(),
            mean_age = mean(Age, na.rm = TRUE),
            sd_age = sd(Age, na.rm = TRUE))%>%
  group_by()%>%
  mutate(total.n = sum(n))

min_age.2 = min(all.data.study2$Age, na.rm = TRUE)
max_age.2 = max(all.data.study2$Age, na.rm = TRUE)
mean_age.2 = mean(all.data.study2$Age, na.rm = TRUE)
sd_age.2 = sd(all.data.study2$Age, na.rm = TRUE)
```


### Participants
Our current sample includes `r demos.2$total.n[1]` children out of a planned sample of 40 ($M_{age}$ = `r round(mean_age.2, 2)` years, $SD_{age}$ = `r round(sd_age.2, 2)` years, range = `r round(min_age.2, 2)` - `r round(max_age.2, 2)` years) recruited in preschools and the surrounding community in San Diego, California, USA. All children were classified as CP-knowers by the Give-N task.

## Procedures
Procedures and tasks were identical to Experiment 1 with two exceptions in the set-matching task. First, because the results of Experiment 1 indicated that children were unable to use one-to-one correspondence with orthogonally oriented sets, boards were only presented in a Parallel orientation, with trial order for larger sets counterbalanced across participants. Second, to test whether CP-knowers' performance could be explained by subvocal counting, after the last trial of set-matching (8 or 10 fish) the experimenter covered both boards and asked the child, "How many fish are in my pond?" If the child did not know, they were prompted to guess. The logic of this follow-up question was that, if the child had succeeded by counting, then they should provide an accurate answer when asked to report the target set's cardinality. To control for differences in working memory, and to test whether children were capable of remembering a recently counted set, the experimenter then let the child count the board, covered it again, and then asked, "How many fish are in my pond?" 

## Results and Discussion
```{r idk_study2, include = FALSE}
##make a df for this
idk.first <- counting.check.df %>%
  filter(Task_item == "Neutral-Final Question")%>%
  mutate(IDK.first = ifelse(str_detect(Response, "IDK", negate = FALSE), 1, 0))%>%
  dplyr::select(SID, IDK.first, Response)%>%
  dplyr::rename(Final_q = Response)

##get the last trial for each kid
last.trial <- counting.check.df %>%
  filter(Trial_number == "5")%>%
  dplyr::select(SID, Task_item, Response)%>%
  dplyr::rename(Num_given = Response)

##now get memory check 
memory.check <- counting.check.df %>%
  filter(Task_item == "Memory_check_answer")%>%
  dplyr::select(SID, Response)%>%
  dplyr::rename("Memory_check" = Response)

##bind all this together
full.check <- left_join(last.trial, idk.first, by = "SID")
full.check <- left_join(full.check, memory.check, by = "SID")

##how many kids passed memory check 
full.check %<>%
  mutate(Task_item = as.character(Task_item), 
         Memory_check = as.character(Memory_check))%>%
  mutate(memory.check.correct = ifelse(Memory_check == Task_item, 1, 0))

mean(full.check$memory.check.correct)
  
## how many said IDK first
sum(full.check$IDK.first)

## of children who did not give IDK response first, how many were correct
numeric.responses <- full.check %>%
  filter(IDK.first != 1)%>%
  mutate(Final_q = as.character(Final_q), 
         correct.verbal.response = ifelse(Final_q == Task_item, 1, 0), 
         delta = abs(as.numeric(Task_item) - as.numeric(Final_q)), 
         delta.given = abs(as.numeric(Final_q) - as.numeric(as.character(Num_given))))

sum(numeric.responses$correct.verbal.response)

## of children who did not give IDK first responses, how far off were they?
mean(numeric.responses$delta)
sd(numeric.responses$delta)

## of children who did not give IDK first responses, how far off were their responses from the number given?
mean(numeric.responses$delta.given)
sd(numeric.responses$delta.given)

## separate numerical group by correct matching, see if there are differences in numerical response
numeric.responses %<>%
  mutate(correct.given = ifelse(Num_given == Task_item, 1, 0))

numeric.responses %>% 
  group_by(correct.given)%>%
  summarise(n = n(),
            mean.delta.verbal = mean(delta), 
            mean.delta.given = mean(delta.given))

## group IDKs and numeric together and look at accuracy 
all.data.study2 <- left_join(all.data.study2, idk.first, by = "SID")

acc.ms <- all.data.study2 %>%
  group_by(SID, IDK.first)%>%
  summarise(mean = mean(Correct, na.rm = TRUE))

t.test(subset(acc.ms, IDK.first == 1)$mean, 
       subset(acc.ms, IDK.first == 0)$mean, var.equal = TRUE)




```

The majority of children (93%) were able to remember the cardinality of a recently counted set. Of the 28 children currently included in this dataset, 15 first responded "I don't know." Of the 13 children who first offered a numeric answer, only 2 gave a correct response. Children who were able to provide a numeric response gave verbal estimates that were, on average, about 4 numbers off from the correct response (*Min* = 1, *Max* = 18, *SD* = 5.5). Additionally, these children did not show evidence of having counted as they were generating their sets, as their verbal responses were almost 5 numbers off from the size of the set they had generated (*M* = 4.92, *SD* = 3.7). Finally, children who gave a numeric response did not have higher overall mean performance in comparison to children who were unable to provide a numeric response (*t*(26) = 0.37, *p* = 0.72). Together, these results suggest that the greater accuracy CP-knowers demonstrated in Experiment 1 was likely not due to subvocal counting. 

```{r}
##overall accuracy for large and small numerosities
#study 1
num.ms.1 <- all.data %>%
  filter(Task == "Parallel", 
         Trial_number != "Training", 
         CP_subset == "CP")%>%
  group_by(Numerosity)%>%
  summarise(mean = mean(as.numeric(as.character(Correct)), na.rm = TRUE), 
            sd = sd(as.numeric(as.character(Correct)), na.rm = TRUE))

#study 2
num.ms.2 <- all.data.study2 %>%
  filter(Task == "Set-matching", 
         Trial_number != "Training")%>%
  group_by(Numerosity)%>%
  summarise(mean = mean(as.numeric(as.character(Correct)), na.rm = TRUE), 
            sd = sd(as.numeric(as.character(Correct)), na.rm = TRUE))
```
Additionally, we found that CP-knowers' set-matching performance closely matched Experiment 1, with `r 100*round(num.ms.2$mean[2], 2)`% accuracy for small numerosities (compared with `r 100*round(num.ms.1$mean[2], 2)`% in Experiment 1), and `r 100*round(num.ms.2$mean[1], 2)`% accuracy for large numerosities (compared with `r 100*round(num.ms.1$mean[1], 2)`% in Experiment 1). 

# General Discussion
Although concepts associated with linguistic expressions such as "\emph{eleven}" are unequivocally tied to symbolic number, it is unknown whether the idea that number \emph{can} be exact is only available through exact number language. Previous work exploring this question has produced conflicting results, with exact number representations sometimes hinging on symbolic number [@gordon2004; @everett2012; @negen2009]; and sometimes being available in its absence [@frank2008; @jaraettinger2017]. In the current work, we returned to this question with a large sample of children to explore whether one diagnostic of exact number -- the ability to use one-to-one correspondence to generate numerically equal matches -- changed as a function of symbolic number acquisition.

By adapting a method previously used in innumerate cultures, we provide a broad and flexible test of children's exact number knowledge at varying stages of their symbolic number acquisition. Our findings help resolve some conflict in the literature, and also provide novel data on the relationship between language and thought in numerical development. We replicate previous findings with the Pirahã and young children that numeracy is related to exact number concepts [@gordon2004; @everett2012; @negen2009]: While both subset and CP-knowers were generally accurate on the set-matching task for quantities within the PI range, only CP knowers were more likely to generate an exact (as opposed to approximate) match for larger quantities. Subset knowers, on the other hand, were unlikely to spontaneously deploy a set-matching strategy that would guarantee exact, rather than approximate, equality. These results shed light on children's acquisition of exact number, and are compatible with the hypothesis that such representations are constructed through mastering the language and procedures of the symbolic number system [@sarnecka2015; @carey2004]. 

A novel finding in this work is that, while CP-knowers were more accurate, their performance was surprisingly variable and well below adult levels [@frank2008]. This indicates that acquiring the CP alone may not be sufficient to furnish a complete understanding of exact number and its relationship to one-to-one correspondence. One possible reason for this noisy performance is that many young CP-knowers may have only a surface-level understanding of counting, and blindly deploy it to generate cardinalities without necessarily grasping its deeper logical entailments and numerical meaning [@barner2017]. Prior work has shown that many children discover other properties of the integers, such as the successor function [@cheung2017], well after acquiring the CP, suggesting that as children progress from a procedural to numerical understanding of the count list, their understanding of exact number similarly grows more robust. Children's performance here raises the possibility that a full understanding of equinumerosity may emerge some time after acquiring the CP. Future work should investigate the trajectory of this understanding, and its implications for the development of other numerical knowledge [@carey2019]. 

There are two important limitations of this work. First, because we wished to provide a measure of children's unprompted attention to exactness, our ambiguous instructions to "Make your pond look like mine" may have created too large a hypothesis space, prompting some children to generate matches on the basis of length, density, or some other set feature. That subset knowers' matching behavior was affected by set identity is consistent with this alternative, and with prior work showing that perceptual identity is more salient than numerical equality for subset knowers [@izard2014; @mix1999], and even some CP-knowers [@chan2017]. Other work has shown that subset knowers perform similarly to CP-knowers on non-symbolic number tasks when emphasizing number over other properties of a set [@negen2015]. Second, the set-matching paradigm does not disambiguate between a successful approximation and an application of one-to-one correspondence. Children's ANS becomes more precise after they acquire the CP [@shusterman2016], leaving open the possibility that CP-knowers' lower rates of error and higher accuracy may reflect some mix of both one-to-one and approximation strategies. These limitations provide direction for future work testing the effects of directing children's attention to number, and also disambiguating between different set-matching strategies.

<!-- Finally an alternative hypothesis to the one advanced here -- that CP-knowers are more likely to spontaneously use one-to-one correspondence after acquiring the CP to establish exact equality for large quantities -- is that children are approximating on this task throughout symbolic number acquisition, and that these approximations slowly grow more accurate. Children's ANS becomes more precise after acquiring the CP [@shusterman2016], which could be related to their increased performance on this task. Although our analyses of children's COVs and error did not indicate this was the case, subsequent work should explore this possibility by explicitly disambiguating children's strategy.  -->

Together, this work provides key data on the previously unclear relationship between language and the origin of exact number concepts. We found that, consistent with the hypothesis that the availability of exact number concepts is linked to exact number language [@nunez2017], children who had limited symbolic number knowledge struggled on a test of exact equality. On the other hand, CP-knowers had significantly greater accuracy, suggesting that acquiring exact number language may, at the very least, make concepts such as exact equality more accessible. While CP-knowers outperformed subset knowers, their accuracy on even the simplest version of this task was surprisingly low, indicating that not all CP-knowers fully grasp Hume's Principle. Future work should explore the development of this knowledge in numerate children, and the process through which children might acquire a more complete understanding of the relationship between one-to-one correspondence and exact number.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
