---
title: "OneOne_analysis"
author: "Rose M. Schneider"
date: "4/10/2018"
output: html_document
---
###Setup
```{r, include = FALSE}
rm(list = ls())
require("knitr")
opts_knit$set(root.dir = "~/Documents/Projects/one-one/") #this is specific to RMS, change accordingly
library(tidyverse)
library(magrittr)
library(langcog)
library(lme4)
library(stringr)
library(RColorBrewer)
library(ggthemes)

'%!in%' <- function(x,y)!('%in%'(x,y))
```

###Load Data
```{r}
data.raw <- read.csv("~/Documents/Projects/one-one/Data/one-one_data.csv")%>%
  filter(SID != "CopyPasteMe")%>%
  droplevels()%>%
  mutate(Age = as.numeric(as.character(Age)), 
         Agegroup = cut(Age, breaks = c(3, 3.5, 4, 4.5, 5.1)))%>%
  mutate(CP_subset = ifelse(Knower_level == "CP", "CP", "Subset"), 
          CP_subset = factor(CP_subset))
```

###Exclusions
```{r}
#how many kids pre-exclusion
data.raw %>% 
  distinct(SID, CP_subset)%>%
  group_by(CP_subset)%>%
  summarise(n = n())

#why are kids excluded?
data.raw %>%
  filter(Exclude == 1)%>%
  distinct(SID, Exclude_reason)%>%
  group_by(Exclude_reason)%>%
  summarise(n = n())

##exclude these kids from analysis
all.data <- data.raw %<>%
  filter(Exclude != 1)

##How many kids?
all.data %>%
  distinct(SID, CP_subset)%>%
  group_by(CP_subset)%>%
  summarise(n = n())
```

##Demographics
```{r}
all.data %>%
  distinct(SID, Age, Knower_level)%>%
  group_by(Knower_level)%>%
  summarise(n = n(), 
            mean_age = mean(Age, na.rm = TRUE), 
            sd_age = sd(Age, na.rm = TRUE))%>%
  kable()

all.data %>%
  distinct(SID, Age, Knower_level)%>%
  ggplot(aes(x = Knower_level, y = Age, fill = Knower_level)) + 
  geom_boxplot() + 
  theme_bw()
```

---

###Data manipulations 
Get counting proficiency for each participant: 
Foor each set (8/10), participants received a score of 3 (perfect); 2 (counted incorrectly but fixed mistake); 1 (counted only a few correctly); 0 (counted randomly)

```{r}
#fix the name of the task for kids who weren't run on two trials of 10
tmp <- all.data %>%
  filter(Task == "How Many")%>%
  mutate(Task_item = ifelse(Task_item == "Score", "10 - Score", as.character(Task_item)))

#compute mean counting
ms.count <- tmp %>%
  filter(Task_item == "10 - Score" | 
           Task_item == "8 - Score")%>%
  distinct(SID, Task_item, Response)%>%
  group_by(SID)%>%
  summarise(count_proficiency = mean(as.numeric(as.character(Response, na.rm = TRUE))))%>%
  dplyr::select(SID, count_proficiency)

##add to all.data
all.data <- right_join(all.data, ms.count, by = "SID")
```

####Get highest count for each participant
```{r}
hc.lookup <- all.data %>%
  filter(Task_item == "Highest_count")%>%
  dplyr::select(SID, Response)%>%
  dplyr::rename(highest_count = Response)

##There are several children who will not count out loud, exclude them from analyses with Highest Count

all.data <- right_join(all.data, hc.lookup, by = "SID")
```

####Classify participants as CP or subset-knowers
```{r}
all.data %<>%
  mutate(CP_subset = ifelse(Knower_level == "CP", "CP", "Subset"))
```

---

#Set-matching tasks
##Visualize parallel and orthogonal set-matching task
```{r}
all.data %>%
  filter(Task == "Parallel" | Task == "Orthogonal") %>%
  filter(Trial_number != "Training")%>%
  mutate(Response = as.integer(as.character(Response)))%>%
  mutate(Task_item = factor(Task_item)) %>%
  ggplot(aes(x = Task_item, y = Response, colour = Correct, group = CP_subset)) +
  geom_count(stroke = 1.2) +
  geom_smooth(se = FALSE, colour = "black") + 
  xlim('3', '4', '6', '8', '10') +
  scale_y_continuous(breaks = seq(1, 15, 1)) +
  theme_bw(base_size = 10) +
  labs(x = "Set size", y = "Number given") +
  langcog::scale_colour_solarized("Correct")+ 
  theme(panel.grid.minor = element_blank())+
  facet_grid(factor(Task, levels = c("Parallel", "Orthogonal"))~CP_subset) + 
  guides(n = 'legend')
```

##Mean performance by group
```{r}
all.data %>%
  filter(Task == "Parallel" | Task == "Orthogonal", 
         Trial_number != "Training")%>%
  mutate(Task_item = factor(Task_item, levels = c("3", "4", "5", 
                                                  "6", "7", "8", "9", "10")))%>%
  group_by(Task, Task_item, CP_subset)%>%
 summarise(mean = mean(as.integer(as.character(Correct)), na.rm = TRUE), 
            n = n(), 
            sd = sd(as.integer(as.character(Correct)), na.rm = TRUE), 
            se = sd/sqrt(n)) %>%
  ggplot(aes(x = Task_item, y = mean, colour = CP_subset, group = CP_subset)) +
  geom_point(size = 2) + 
  geom_line() +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), 
                width = .1) +
  theme_bw(base_size = 13) + 
  facet_grid(~factor(Task, levels = c("Parallel", "Orthogonal")), scale = "free_x") +
  theme(legend.position = "right", 
        legend.title = element_blank()) +
  labs(x = "Set size", y = "Mean performance") +
  scale_colour_brewer(palette = "Dark2") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  
```

##Visualization by condition (Identical/Non-Identical)
```{r}
all.data %>%
  filter(Task == "Parallel" | Task == "Orthogonal", 
         Trial_number != "Training")%>%
  mutate(Task_item = factor(Task_item, levels = c("3", "4", "5", 
                                                  "6", "7", "8", "9", "10")))%>%
  group_by(Task, Task_item, Condition, CP_subset)%>%
 summarise(mean = mean(as.integer(as.character(Correct)), na.rm = TRUE), 
            n = n(), 
            sd = sd(as.integer(as.character(Correct)), na.rm = TRUE), 
            se = sd/sqrt(n)) %>%
  ggplot(aes(x = Task_item, y = mean, colour = CP_subset, group = CP_subset)) +
  geom_point(size = 2) + 
  geom_line() +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), 
                width = .1) +
  theme_bw(base_size = 13) + 
  facet_grid(Condition~factor(Task, levels = c("Parallel", "Orthogonal")), scale = "free_x") +
  theme(legend.position = "right", 
        legend.title = element_blank()) +
  labs(x = "Set size", y = "Mean performance") +
  scale_colour_brewer(palette = "Dark2") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  
```

##Visualization of mean absolute error by knower-level for each task 
Make a mean error df
```{r}
error.df <- all.data %>%
  filter(Task == "Parallel" | Task == "Orthogonal", 
         Trial_number != "Training")%>%
  droplevels()%>%
  mutate(Task_item = as.numeric(as.character(Task_item)), 
         Response = as.numeric(as.character(Response)), 
         abs_error = abs(Task_item-Response))
```

```{r}
error.df %>%
  filter(Correct == "0")%>%
  mutate(Task_item = factor(Task_item, levels = c("3", "4", "5", 
                                                  "6", "7", "8", "9", "10")))%>%
  group_by(Task, Task_item, CP_subset)%>%
 summarise(mean_error = mean(abs_error, na.rm = TRUE), 
            n = n(), 
            sd = sd(abs_error, na.rm = TRUE), 
            se = sd/sqrt(n)) %>%
  ggplot(aes(x = Task_item, y = mean_error, colour = CP_subset, group = CP_subset)) +
  geom_point(size = 2) + 
  geom_line() +
  geom_errorbar(aes(ymin = mean_error - se, ymax = mean_error + se), 
                width = .1) +
  theme_bw(base_size = 13) + 
  facet_grid(~factor(Task, levels = c("Parallel", "Orthogonal")), scale = "free_x") +
  theme(legend.position = "right", 
        legend.title = element_blank()) +
  labs(x = "Set size", y = "Mean absolute error") +
  scale_colour_brewer(palette = "Dark2") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  
```

##Visualization of mean absolute error by condition
```{r}
error.df %>%
  filter(Correct == "0")%>%
  mutate(Task_item = factor(Task_item, levels = c("3", "4", "5", 
                                                  "6", "7", "8", "9", "10")))%>%
  group_by(Task, Task_item, CP_subset, Condition)%>%
 summarise(mean_error = mean(abs_error, na.rm = TRUE), 
            n = n(), 
            sd = sd(abs_error, na.rm = TRUE), 
            se = sd/sqrt(n)) %>%
  ggplot(aes(x = Task_item, y = mean_error, colour = CP_subset, group = CP_subset)) +
  geom_point(size = 2) + 
  geom_line() +
  geom_errorbar(aes(ymin = mean_error - se, ymax = mean_error + se), 
                width = .1) +
  theme_bw(base_size = 13) + 
  facet_grid(Condition~factor(Task, levels = c("Parallel", "Orthogonal")), scale = "free_x") +
  theme(legend.position = "right", 
        legend.title = element_blank()) +
  labs(x = "Set size", y = "Mean absolute error") +
  scale_colour_brewer(palette = "Dark2") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  
```

##Counting proficiency
Scatterplot of age and counting proficiency
```{r}
all.data %>%
  filter(!is.na(count_proficiency), 
         count_proficiency != 5) %>% #temporary, coding issue
  distinct(SID, CP_subset, Age, count_proficiency)%>%
  mutate(count_proficiency = factor(count_proficiency))%>%
  ggplot(aes(x = count_proficiency, y = Age, color = count_proficiency, gorup = count_proficiency)) + 
  geom_point() + 
  theme_bw() + 
  facet_grid(~CP_subset)
```

Barplot by knower-level
```{r}
all.data %>%
  filter(!is.na(count_proficiency), 
         count_proficiency != 5) %>% #temporary, coding issue
  distinct(SID, CP_subset, Age, count_proficiency)%>%
  mutate(count_proficiency = factor(count_proficiency))%>%
  ggplot(aes(x = CP_subset, fill = count_proficiency)) + 
  geom_histogram(stat = "count") + 
  theme_bw()
```

##Highest count
```{r}
all.data %>%
  filter(!is.na(highest_count))%>%
  mutate(highest_count = as.numeric(as.character(highest_count)))%>%
  distinct(SID, Age, CP_subset, highest_count)%>%
  ggplot(aes(x = highest_count, fill = CP_subset)) + 
   geom_histogram(color = "black", stat = "count")+
  theme_bw() + 
  scale_fill_brewer(palette = "Set1") + 
  labs(x = "Highest Count (unprompted)", y = "Count")
```

---

#Analyses

